How fluid-mechanical erosion creates anisotropic porous media

### 2022-06-29 docs/PhysicsPaper/StokesErosion.tex
NM

In this paper, we have presented a Cauchy formulation of the boundary integral equation method to simulate the fluid-mechanical erosion of many bodies in a Stokes flow. The accuracy and efficiency of the method enables high-fidelity simulations of dense suspensions of $O(100)$ bodies and statistical analysis across an ensemble of different initializations. By linking the governing Stokes equations to Darcy's law, we are able to extract porous media properties, including permeability, resistivity, tortuosity, and anisotropy, as they evolve over time. Direct comparison between the resistivity and the total drag force confirms such bulk properties are extracted with high accuracy.

>>>>

In this paper, we have presented a Cauchy formulation of the boundary integral equation method to simulate the fluid-mechanical erosion of many bodies in a Stokes flow. The accuracy and efficiency of the method enables high-fidelity simulations of dense suspensions of $O(100)$ bodies and statistical analysis across an ensemble of different initializations. By linking the governing Stokes equations to Darcy's law, we are able to extract porous-media properties, including permeability, resistivity, tortuosity, and anisotropy, as they evolve over time. Direct comparison between the resistivity and the total drag force confirms such bulk properties are extracted with high accuracy.
